Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text

Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3. The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet. Using ESBMC with Boolector led to an out of memory situation in all the case studies. This result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}. However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies. Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s. However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, \textcolor{red}{which is in Line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code (much more complex)}.

>>>>

Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3. The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet. Using ESBMC with Boolector led to an out of memory situation in all the case studies. This result was obtained in less than six minutes of execution, i.e., the 64 G bytes of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}. However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies. Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 4m27s to 5m08s. However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
This verification took less than 1s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in Line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code (much more complex).
